On The Impact of Atoms of Confusion in JavaScript Code

### 2020-11-11 1_Introduction.tex
mais uma revisao da secao de introducao

JavaScript is the most widely used language for web development and the most often adopted language on GitHub~\cite{BugsJS:ICST}. At the same time, JavaScript is infamously known to be ``the worst most popular language in the world''\footnote{https://github.com/getify/You-Dont-Know-JS/blob/2nd-ed/preface.md}. It is a weakly typed language~\cite{DynamicBehaviorJS:PLDI} that provides object-oriented, functional, and imperative constructs~\cite{JS-CodeSmells:SCAM}, in addition to features such as run-time evaluation~\cite{BugsJS:ICST, ClientSideBugsJS:TSE}, and asynchronous operations. All these 
%diverse characteristics and capabilities
features combined make JavaScript source code fertile ground for errors~\cite{BugsJS:ICST, ClientSideBugsJS:TSE} and confusion~\cite{JSGoodParts:book}.

Our research aims to help practitioners identify potentially confusing snippets of code and replace them with clearer code.
% Developers could improve their codebases' understandability by following our recommendations.
To achieve that, we characterize a set of 9 JavaScript \emph{atoms of confusion}; small pieces of code that hinder developers' understanding of the source code of a program for which there are functionally equivalent alternatives that are easier to understand~\cite{DBLP:conf/sigsoft/GopsteinIYDZYC17}.\castor{I think it would be really nice to have an example here. Maybe even a figure with a left-hand and a right-hand side. What do you say? If yes, I
'd go for post increment or assignment as value. If not a figure, the text could be as follow: An example of atom of confusion identified by previous work~\cite{DBLP:conf/sigsoft/GopsteinIYDZYC17} is the use \texttt{if} statements without the accompanying curly braces. The alternative, in this case, is simply to always use the curly braces.}
Among the atoms in this work, X are shared between JavaScript and \clang/\cpplang (e.g., pre/post-increment), while Y others are specific to JavaScript, e.g., the atom Assignment as Value.
Recent work~\cite{DBLP:journals/ese/MedeirosLAAKRG19,DBLP:conf/sigsoft/He19,DBLP:conf/sigsoft/GopsteinIYDZYC17} has already explored the impact of atoms of confusion on program understanding,
and confirmed they negatively impact source code understandability.
However, they were constrained to statically typed languages.
To the best of our knowledge, we are the first to explore atoms of confusion in the context of a dynamically typed language (JavaScript).\castor{Review the number of atoms, X, and Y.}

\diego{"Understanding source code comments at large-scale"\cite{DBLP:conf/sigsoft/He19} (acima): 
embora relacionado não me parece um estudo de átomos de confusão}

To understand whether an atom of confusion introduces misunderstandings, we surveyed 150 developers from the Reddit community. Their task was to predict the output of short snippets of code, with half of them containing atoms of confusion. We found that the presence of the Comma Operator atom can increase the average time to predict the output by 65\%, while the behavior of snippets containing the Pre-Increment atom were predicted 44\% faster.  An atom's presence---or lack of---in open-source repositories may reveal cases where developers should be more or less careful when writing code. To identify such cases, we mined the 100 most popular JavaScript projects from GitHub and found a total of X atoms in the analyzed projects. To learn more about the misunderstandings in the snippets used in the survey, we interviewed 15 experienced professional developers. Participants preferred code snippets \textit{without} an atom in 70\% of the cases, therefore corroborating to the survey findings.\castor{It would be nice to have results about correctness.}

>>>>

JavaScript is the most widely used language for web development and the most often adopted language on GitHub~\cite{BugsJS:ICST}. At the same time, JavaScript is infamously known to be ``the worst most popular language in the world''\footnote{https://github.com/getify/You-Dont-Know-JS/blob/2nd-ed/preface.md}. It is a weakly typed language~\cite{DynamicBehaviorJS:PLDI} that provides object-oriented, functional, and imperative constructs~\cite{JS-CodeSmells:SCAM}, in addition to features such as run-time evaluation~\cite{BugsJS:ICST,ClientSideBugsJS:TSE}, and asynchronous operations. All these 
%diverse characteristics and capabilities
features combined make JavaScript source code fertile ground for errors~\cite{BugsJS:ICST,ClientSideBugsJS:TSE} and confusion~\cite{JSGoodParts:book}.

Our research aims to help practitioners identify potentially confusing snippets of code, so that
developers could replace them with clearer code.
To achieve that, we investigate {\color{red}XYZ} JavaScript idioms that
might compromize program understanding. These idioms correspond to a set of candidates for \emph{atoms of confusion} in
JavaScript---that is, small
pieces of code that hinder developers' understanding of the source code of a program
for which there are functionally equivalent alternatives that are easier
to understand~\cite{DBLP:conf/sigsoft/GopsteinIYDZYC17}. \castor{I think it would be really nice to have an example here. Maybe even a figure with a left-hand and a right-hand side. What do you say? If yes, I
'd go for post increment or assignment as value. If not a figure, the text could be as follow: An example of atom of confusion identified by previous work~\cite{DBLP:conf/sigsoft/GopsteinIYDZYC17} is the use \texttt{if} statements without the accompanying curly braces. The alternative, in this case, is simply to always use the curly braces.}
Among the atoms in this work, X are shared between JavaScript and \clang/\cpplang (e.g., pre/post-increment), while Y others are specific to JavaScript, e.g., the atom Assignment as Value.
Recent work~\cite{DBLP:journals/ese/MedeirosLAAKRG19,DBLP:conf/sigsoft/GopsteinIYDZYC17} has
already explored the impact of atoms of confusion on program understanding,
and confirmed they negatively impact source code understandability.
However, they were constrained to statically typed languages (e.g., C and C++).
To the best of our knowledge, we are the first to explore atoms of confusion
in the context of a dynamically typed language (JavaScript).\castor{Review the number of atoms, X, and Y.}

To understand whether an atom of confusion introduces misunderstandings, we surveyed 140 developers from the Reddit community. Their task was to predict the output of short snippets of code, with half of them containing atoms of confusion. We found an improvement of at least 15\% in the correct answers when removing the confusing code for seven atoms (out of 9 atoms). The presence of the Comma Operator atom, for instance, can increase the average time to predict the output by 65\%, while the behavior of snippets containing the Pre-Increment atom were predicted 44\% faster.  An atom's presence---or lack of---in open-source repositories may reveal cases where developers should be more or less careful when writing code. To identify such cases, we mined the 100 most popular JavaScript projects from GitHub and found a total of X atoms in the analyzed projects. To learn more about the misunderstandings in the snippets used in the survey, we interviewed 15 experienced professional developers. Participants preferred code snippets \textit{without} an atom in 70\% of the cases, therefore corroborating to the survey findings. During the MSR and interview studies, we also explored additional atom candidates that are specific to the
JavaScript language.
